Paper notes

### 2019-08-09 paper_notes.Rmd
ok symmetric decreasing slope

f_eth <- function(i_e,M,x,n,S){
  if (x > n){
    U <- NA}else{
  if (x < round(n*i_e,digits = 2)){
   U <- (x / round((n*i_e),digits = 2)) * S
    }else if (x > round((n*i_e),digits = 2)){
      U <- M + ((1- round((x/n),digits = 2))*(1-M))/(1-i_e)
    }else{
        U <- 1}
  round(U,digits = 2)
    }
}

@@

A <- data.frame(x_graph,utility_location,funct_symm)

@@

write.csv2(A,file="C:/Users/rocpa/OneDrive/Desktop/08_08_2019/ethnic-value_multinomial/data_utility")

A_graph <- ggplot(A,aes(x_graph,utility_location))

@@

S_0 <- c(0,0,0,0,0,NA,NA,NA,NA)
M_1 <- c(NA,NA,NA,NA,1,1,1,1,1)
S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
M_0 <- c(NA,NA,NA,NA,1,0.76,0.5,0.24,0)  # should be 0.75 and 0.24, I think due to round(U)2 in the function

@@

i_e = 0.5
M = 0
S = 1
n = 7

>>>>

f_eth <- function(i_e,M,x,n,S){
  if (x > n){
    U <- NA}else{
  if (x < round(n*i_e,digits = 2)){
   U <- (x / round((n*i_e),digits = 2)) * S
    }else if (x > round((n*i_e),digits = 2)){
      U <- M + ((1- (x/n))*(1-M))/(1-i_e)   
    }else{
        U <- 1}
  round(U,digits = 2)
    }
}

@@

A <- data.frame(x_graph[c(0:9)],utility_location[c(0:9)],funct_symm[c(0:9)])

@@

# write.csv2(A,file="C:/Users/rocpa/OneDrive/Desktop/08_08_2019/ethnic-value_multinomial/data_utility")

A_graph <- ggplot(A,aes(x_graph[c(0:9)],utility_location[c(0:9)]))

A_graph + geom_point()

@@

S_0 <- c(0,0,0,0,0,NA,NA,NA,NA)
M_1 <- c(NA,NA,NA,NA,1,1,1,1,1)
S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
M_0 <- c(NA,NA,NA,NA,1,0.75,0.5,0.25,0)  # should be 0.75 and 0.24, I think due to round(U)2 in the function

@@
